---
title: "Homework 5"
author: "Yujin Zhang"
output: github_document
---

```{r}
library(tidyverse)
library(ggplot2)
```

## Problem 1

Describe the raw data. Create a city_state variable (e.g. “Baltimore, MD”) and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”).

```{r}
homicide_df = 
  read_csv("./data/homicide-data.csv", na = c("", "Unknown")) %>% 
  janitor::clean_names() %>% 
  mutate(
    city_state = str_c(city, state),
    resolution = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest" ~ "unsolved",
      disposition == "Closed by arrest" ~ "solved",
    )
         ) %>% 
  relocate(city_state) %>% 
  filter(city_state != "TulsaAL")
```

For the city of Baltimore, MD, use the prop.test function to estimate the proportion of homicides that are unsolved; save the output of prop.test as an R object, apply the broom::tidy to this object and pull the estimated proportion and confidence intervals from the resulting tidy dataframe.

```{r}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "BaltimoreMD")

baltimore_summary =
  baltimore_df %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  )

# make prop.test
baltimore_test =
  prop.test(
  x = baltimore_summary %>% pull(unsolved),
  n = baltimore_summary %>% pull(n)
  )

# organize the data frame
baltimore_test %>% 
  broom::tidy()

```

Now run prop.test for each of the cities in your dataset, and extract both the proportion of unsolved homicides and the confidence interval for each. Do this within a “tidy” pipeline, making use of purrr::map, purrr::map2, list columns and unnest as necessary to create a tidy dataframe with estimated proportions and CIs for each city.

```{r}
# create function for prop.test
prop_test_function = function(city_df) {
  
  city_summary =
    city_df %>% 
    summarize(
      unsolved = sum(resolution == "unsolved"),
      n = n()
  )

  # make prop.test
  city_test =
    prop.test(
      x = city_summary %>% pull(unsolved),
      n = city_summary %>% pull(n)
    )

  return(city_test)
  
}

homicide_df %>% 
  filter(
    city_state == "BaltimoreMD"
  ) %>% 
  prop_test_function()

```

Then run prop.test for each of the cities in dataset.

```{r}
nested_df = 
  homicide_df %>% 
  nest(data = uid:resolution) %>% 
  mutate(
    test_result = map(data, prop_test_function),
    tidy_result = map(test_result, broom::tidy)
    ) %>% 
  select(city_state, tidy_result) %>% 
  unnest(tidy_result) %>% # unnest the data frame
  select(city_state, estimate, starts_with("conf"))

```

Create a plot that shows the estimates and CIs for each city – check out geom_errorbar for a way to add error bars based on the upper and lower limits. Organize cities according to the proportion of unsolved homicides.

```{r}
# make errorbar plot
nested_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state,y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))

```

## Problem 2

Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:

Start with a dataframe containing all file names.Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe.

Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary.

```{r}
# make function to read data in files
read_data_function = function(file_df) {
  
  patient_df = 
    read_csv(file_df)
  
  return(patient_df)
}

# create a data frame containing all participants
longitudinal_df =
  tibble(
    files = list.files("./data/p2data")
  ) %>% 
  mutate(
    path = map(.x = files, ~paste("./data/p2data", ., sep = "/"))
  ) %>%                                                             # add path
  mutate(files = str_extract(files, "[conexp]{3}_[0-9]{2}")) %>%    # delete ".csv"
  separate(
    files, into = c("arm", "subject_id", sep = "_")) %>%            # add participants variable
  mutate(
    observations = map(path, read_data_function)) %>% 
  select(-"_")

# show data frame
longitudinal_df
```
 
Then I tidy the results.

```{r}
#unnest the list variable
unnest_df =
  longitudinal_df %>% 
  unnest(cols = "observations") %>% 
  select(-path)

# show table
knitr::kable(unnest_df)
  
```

Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.

```{r}
plot_df =
  unnest_df %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    names_prefix = "week_",
    values_to = "obs_value"
  ) 

# make spaghetti plot
plot_df %>% 
  group_by(arm) %>% 
  ggplot(aes(x = as.numeric(week), y  = obs_value, color = subject_id)) +
  geom_line() +
  facet_grid(.~arm) +
  labs(
    title = "Spaghetti Plot for Arms in 8 Weeks",
    x = "Week",
    y = "Value",
    ) 
  
  
```


## Problem 3
Write a function that takes a vector as an argument; replaces missing values using the rules defined; and returns the resulting vector. Apply this function to the columns of iris_with_missing using a map statement.

There are two cases to address:

For numeric variables, fill in missing values with the mean of non-missing values.
For character variables, fill in missing values with "virginica".

```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))

```

Create missing data function

```{r}
fill_in_missing = function(vector) {
  
  if (is.numeric(vector)) {
    
    vector =
      vector %>% 
      replace_na(mean(vector[!is.na(vector)]))
    
  }
  
  if (is.character(vector)) {
   
    vector = 
      vector %>% 
      replace_na("virginica")
    
  }
  
  return(vector)
}

```

Mapping the missing data

```{r}
iris_without_missing =
  map_df(.x = iris_with_missing, ~ fill_in_missing(.x))

iris_without_missing
```

